Circumnuclear Media and Accretion Rates of Quiescent Supermassive Black Holes

### 2015-04-07 ms.tex
conclusions 10

\item Stellar wind heating, supernovae, and AGN feedback depend explicitely on the SMBH mass as well as the star formation history in the galactic nuclear region.  A recent star burst of age $\lesssim 10$ Myr produces mass and energy injection dominated by young stellar winds ($v_w \sim 1000$ km s$^{-1}$), while for an exclusively old stellar population, mass input is dominated by AGB winds and heating is dominated by AGN feedback and supernovae.  Ongoing, continuous star formation presents a hybrid situation: energy input is usually dominated by young stars, while mass input is dominated by the old stellar population (Appendix \ref{app:windheat}).  Galactic nuclei harboring low mass black holes $\Mbh \lesssim 10^8\Msun$ experiencing star formation histories to match their average derived from cosmological simulations receive stellar wind heating of $v_w\sim 800$ km s$^{-1}$.

>>>>

\item Stellar wind heating, supernovae, and AGN feedback depend explicitely on the SMBH mass as well as the star formation history in the galactic nuclear region.  A recent star burst of age $\lesssim 10$ Myr produces mass and energy injection dominated by young stellar winds ($v_w \sim 1000$ km s$^{-1}$), while for an exclusively old stellar population, mass input is dominated by AGB winds and heating is dominated by AGN feedback and supernovae.  Ongoing, continuous star formation presents a hybrid situation: energy input is usually dominated by young stars, while mass input is dominated by the old stellar population (Appendix \ref{app:windheat}).  Galactic nuclei with $\Mbh \lesssim 10^8\Msun$ that experience heating corresponding to their average star formation histories from cosmological simulations receive stellar wind heating of $v_w\sim 800$ km s$^{-1}$.
